Analyzing TA Comments on Student Writing in R

### 2018-11-30 course_notes.Rmd
updates

# Session 1 (Oct. 1, 2018)
Change

@@

# Session 3 (Nov. 12, 2018)
I have 11,000 comments from TAs on student reports. I want to parse them into topic groups more or less automatically, using pre-defined criteria. What are the options?

@@

	https://www.tidytextmining.com/topicmodeling.html

Challenge is that I have groups **already based on the existing coding book.** The individual groups are already labeled. LDA uses clustering based on its own analysis.

@@

What if I treated each of the pre-defined sub-sets from primary codebook analysis as if they are tweets from separate users? 
	https://www.tidytextmining.com/twitter.html

@@

@@

# Session 4 (Dec. 3, 2018)

>>>>

# Session 1 (Oct. 1, 2018)

@@

# Session 3 (Nov. 12, 2018)
I have 11,000 comments from TAs on student reports. Process for bringing in the tidied data and structuring it for analysis is not done, but is coming along.

I want to sort TA comments into topic groups more or less automatically, using pre-defined criteria. What are the options?

@@

The approach is described here:
	https://www.tidytextmining.com/topicmodeling.html

Challenge is that my groups are **already based on the existing coding book.** The individual groups are already labeled. LDA clusters items based on its own analysis.

@@

What if I treated each of the pre-defined sub-sets of comments I created using codebook analysis as if they were tweets from separate users? That approach is described here: 
	https://www.tidytextmining.com/twitter.html

@@

**Option: Comparison Modeling Via Text Classification**

What if I treated each of the comments as text blocks where pre-defined words are more or less likely to be associated with the category. Jerid developed a Shiny app that does something similar:
https://francojc.github.io/2015/08/15/generating-annotated-text-in-shiny/

@@

# Session 4 (Dec. 3, 2018)
Looking at Jerid's Intro to Statistical Thinking clarified some issues in my approach. I definitely need to be thinking about this problem more in terms of unsupervised exploration.

That leads to my follow-up question: training with 80% seems excessive. If there is a large dataset, is there any cost or benefit to splitting to 33/33/34%, or even 25% x 4? The 80/20 and 60/20/20% seem out of balance, but there is probably logic I do not see.

In the exploration phase, is re-sampling such a major concern?

**Confidentiality Problem**
My initial dataset contains confidential information that needs to be de-identified. How do I convert the data so it can be displayed on a public site?

Most direct solution is to write bridge scripts. The versions that actually read my data in private repo. The public versions of these scripts would have 1+ empty placeholder spaces in the key commands that read in the data. Script documentation would explain how others can modify the bridge script file paths.

I assume that without correct system paths, outside users would not be able to access them. I can provide the de-identified data publicly, without exposing the confidential data.

Any gaps or problems with this approach?

**What Are the Primary Data Keys For Structuring the Dataset?**
These are values that are present already in the dataset.

*record.id*  
Column is a semester ID and 5-digit number, like sp18.00001. This particular record.id indicates the data line is from Spring 2018 CSV file, and is line 00001 of the data table. This should be the unique primary key value for each record. Once assigned, it should not change.

*report.id*  
Format is R\_nnn(...). The string is assigned to each entry made in Qualtrics. This particular string is assigned when a report is collected by our system. It is anonymous, and serves as a unique id for each REPORT document that we collect.

*student*  
The email address of the SUBMITTING STUDENT. Unique to each student, and assigned by WFU. The email address connects multiple reports to a SINGLE STUDENT AUTHOR. It is NOT confidential though, so needs to be switched out.

*ta*  
The name of the TA assigning scores. Unique to instructor, and connects multiple reports scored by SINGLE TA. Again it is NOT confidential, so also needs to be switched out.

Consider either:

* Creating lists of non-repeating IDs with S\_nnn(...) = Student name, T\_nnn(...) = TA name. Then assign the names via a "lookup" style function
* Using a global names generator to build 25K list of randomly generated non-repeating first_last names. In practice, random names are easier to scan for visually.

**Lagniappe**
Maybe it is just me, but I've been struggling with some of the outside instructional materials becuase they use generic terms in ways that make code structure more confusing.

For example, using either "text" or "word" as a variable_name is confusing if the same word is used as part of commands. An example I found of this is when I tried to use the "unnest_tokens" command. Look at the language below from one of the exercises; are the terms inside the parentheses variable_names, or modifiers for the command?

```
(text_tibble) %>% 
  unnest_tokens(word,text)
```

 Just adding a numeral to show it is a variable name would help. For example, "text_1" clearly is not a command or modifier term.

Maybe this goes back to developing a habit of adopting one approach (like snake_case, or never using "_" as the first character in a filename) and sticking to it.

>Thank you x^y times over for the Regex101 link! Getting Regex right has been a pain for me! This greatly simplifies the process.

**Miscellaneous To Do**

* Need to review map, cast and bind commands again. Not sticking in my head.
* Try visualizing the 2-D array of the TA comments as a mosaic plot.

**Marking Lab Reports (random thoughts on a different project)**

Text files for processed lab reports already are structured so we can use them like corpus files with inline meta-data. All lab reports have this as embedded metadata up front:

* Number of lab report in semester: first
* This is a revision.
* Date submitted: 2018-11-06 12:17:40
* Author of this lab report is: *Student's NAME*
* ID: R_1et5dvwqfl2ZCX1
* Course number: 214
* TA: *TA's NAME*

Again, the main change we would need to make is to de-identify the student and TA. In theory I should be able to build some kind of direct replace functions for the TA-name and the Student-name.

### 2018-11-30 index.Rmd
updates

#### \   
## Specific Project Goals
An existing Unix-based script can extract TA comments and meta-data for each student report then assemble the data into a CSV file. Classifying TA comments by hand is impractical for routine use though; 10-12,000 score-able comments are generated EACH SEMESTER. An automated classification method is needed both for speed and consistency.

@@

1. **Creates a de-identified dataset.** Required data will be extracted from the master dataset and organized in an anonymized data frame where all names, comments, and confidential metadata are re-keyed to unique random identifiers.
2. **Classifies TA comments according to our existing codebook**. Initially I will be evaluating whether terms frequencies can be used to classify comments. The goal is to be able to assign instructor comments into our pre-defined Subject and Structure codes with 90% accuracy or greater 
3. **Sorts TA comments using unsupervised grouping methods**. The codebook for classifying TA comments makes prior assumptions about most relevant features. Unsupervised grouping may uncover more robust or informative classification methods.

>>>>

#### \   
## Specific Project Goals
TA comments and meta-data for each student report can be extracted and compiled into a CSV datafile using an existing Unix script. However routinely classifying TA comments by hand is impractical; 10-12,000 comments need to be scored EACH SEMESTER. An automated classification method is needed both for speed and consistency.

@@

1. **Creates a de-identified dataset.** Required data will be extracted from the master CSV data set and organized in an anonymized data frame where all names, comments, and confidential metadata are re-keyed to unique random identifiers.
2. **Classifies TA comments according to our existing codebook**. The goal is to be able to assign instructor comments into our pre-defined Subject and Structure codes with 90% accuracy or greater. Initially I will be evaluating whether terms frequencies can be used to classify comments. Other methods will be evaluated as they come to light. 
3. **Sorts TA comments using unsupervised grouping methods**. The codebook for classifying TA comments makes prior assumptions about most relevant text features. Unsupervised learning may uncover more robust or informative classification groups.

### 2018-11-30 questions.rmd
updates

Ideas?

@@

# Github
#### When I work on Github, I see no easy way to create new file folders.

If I empty a folder, it is deleted automatically. Am I overlooking tools, or is goal to be working locally to create files and use web interface less often?

#### I am not sure how to clone and blend my OWN repos. 
I was trying to build a starting point with both data code and web site pieces by cloning the web site repo, then adding the standard data layout folder. Could not see an obvious way to clone one of my own, or to blend two into one.

#### Question about fork and branch. 
When I fork another repo, I get comments saying I am "#" steps ahead of it. Should I clone instead?

@@

#### Having a slight problem with Git on laptop.
I can use my desktop and create repos to Dropbox or local machine from GitHub. Laptop throws in an extra step that seems to corrupt process.

**SOLVED**. The path to Git was wrong. Needs to be very specific: 
/usr/local/git/bin/git

Other Git and Git-GUI paths do not work.

>>>>

Ideas? Detailed notes are in "Data_intake_1.rmd", starting Line 102.

#### Why can I not append the read.csv command?
This works fine:
```{r}
base_data <- read_csv(file='data/coded_full_comments_dataset_Spring18.csv')
head(base_data)
```

This fails:
```{r}
base_data <- read_csv(file='data/coded_full_comments_dataset_Spring18.csv', header=FALSE)
head(base_data)
```
I get:
```	
	Error in read_csv(file = "data/coded_full_comments_dataset_Spring18.csv",  : 
  unused argument (header = FALSE)
```

@@

# Github
#### Question about fork and branch. 
When I fork another repo, I get comments saying I am "#" steps ahead of it. Should I clone instead?

@@
